Instructions for \confname{} Proceedings

### 2019-05-14 papers/EMNLP2019/data-collection.tex
comments in intro on object naming in realistic scenes/context, needs to made a bit stronger maybe
pass over sect 2.1, sampling of images

We take data from \vgenome \cite{krishna2016visualgenome}, which aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
It contains a dense region-based labeling of $108k$~images with textual expression of the attributes and references of objects, their relationships as well as question answer pairs, all linked to WordNet synsets \cite[see below]{fellbaum1998wordnet}.

% \gbt{START to be refined -- taken from sivl submission as is}

% \vgenome \cite{krishna2016visualgenome} aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
% It contains a dense region-based labeling of $108k$~images with textual expression of the attributes and references of objects, their relationships as well as question answer pairs, all linked to WordNet synsets \cite[see below]{fellbaum1998wordnet}.

% \begin{itemize}
%      		\item[(1)] \textbf{Specific categories}: are not available, as object categories and names are not consistently annotated (and even conflated)
% 				\item[(2)] \textbf{Exhaustive annotations}: are available, which is a huge advantage of this data sets
% 		   \item[(3)] \textbf{Natural names}: are available, though object names might not be fully discriminative (as in referring expressions)

% \end{itemize}
% \gbt{END to be refined -- taken from sivl submission as is}

\subsection{Sampling of Instances (Images/Objects)}

We aimed at collecting a relatively large amount of naturalistic images (\textit{instances}) that depict common objects.
 % of frequent classes/names in  \vgenome, which, at the same time, have been frequently/commonly studied in the psycholinguistic literature. 
%Criteria: From CV: select images depicting objects with relatively frequent names; From CogSci: select objects which have been frequently studied in cognitive science/psychological norming studies; we chose McRae et al. as basis.
We start from the concepts of McRae et al.'s feature norms (REF), which are common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}) and, as such, have a high overlap with standard datasets of object norming studies (REFS).
We added the \textsc{person} category because it is very frequent category in \vgenome.

(As appropriate: We use image and object interchangeably in the following, since we only selected one target object per image (i.e., each object and image in VG is chosen at most once).)

\paragraph{Collection nodes}
% Standard taxonomies do not align well with name variability; for instance, people use more varied names for types of dogs than for types of cows, while both dogs and cows are mammals.
We defined a set of \textit{collection nodes} which we would then use to collect our object instances from VG.

We based the definition of our set of nodes on the WN (REF) synsets of the McRae concepts (e.g.,~dog, duck, goose, gull), the nominal WordNet hierarchy, and the frequency distribution of the VG object names' synsets.\footnote{TODO: need to be clear from the general description of VG that the frequ. of instances labeled with the synset of the object name is meant.}

First, we selected a set of collection node candidates---synsets which match (e.g.,~\textsl{dog, duck, goose, gull}) or subsume (e.g.,~\textsl{mammal, bird}) the McRae synsets\footnote{Specific synset IDs, e.g.,~dog.n.01, are omitted for readability.}. 
From these candidates we kept those as collection nodes which had a high frequency of VG object instances of different names. For example, VG instances  subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck, goose}, or \textsl{gull} did not have name variants in VG, so we kept \textsl{dog} and \textsl{bird} as collection nodes.

\paragraph{Collection of instance candidates}
Goal of above procedure was the collection of instances of selected object classes---our nodes--- whose VG names correspond to or subsume (are hypernyms of) a McRae concept, and whose object names differ, that is, of which we can expect that people possess different names for them (e.g.,~\textsl{duck, goose, gull} for \textsl{bird}).
The collection of such instances using the nodes was then straightforward: We retrieved all VG images  depicting an object whose name matches or is subsumed by one of the collection nodes. 
We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{(REF to tagger)}, or that were multi-word expressions/phrases (e.g.,~\textsl{pink bird}). 
We further only considered objects whose bounding box\footnote{TODO: need to be clear from the general description of VG what is meant.} had an area of~$20-90\%$ of the whole image area.

\paragraph{Sampling of instances}
Finally, from this set of instances we sampled our final dataset of $31,093$~instances. 
Sampling proceeded in dependence on the overall size of the individual collection seeds: 
up to~$800$ objects per seed: all instances, but at most 500, are collected; more than~$800$ objects per seed: all instances, but at most~$1,000$, are collected.  \textbf{double-check}

\cs{END @ GBT}

Table~\ref{tab:XXX} gives an overview of the collection nodes, XXX, XXX, grouped into $7$~domains. (\textbf{Report only dataset after round0, with a note in caption/footnote referring to the checkpoint pruning.})
\gbt{I would put only a table with the final dataset, not the intermediate one (round0). That is, include a table with the 25K imgs (the 30K imgs were just our initial pool).}

@@

\begin{table*}
\small
	\begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
	\toprule
	        animals\_plants &               vehicles &                        home &                clothing &                   buildings &                    food &                 people \\
	\midrule
	  ungulate.n.01 (2037) &  aircraft.n.01 (1208) &  furnishing.n.02 (5355) &  shirt.n.01 (968) &  house.n.01 (364) &  dish.n.02 (812) &  woman.n.01 (1768) \\
	 horse.n.01 (833) &  train.n.01 (957) &  vessel.n.03 (525) &  overgarment.n.01 (786) &  bridge.n.01 (297) &  baked\_goods.n.01 (770) &  man.n.01 (1167) \\
	  feline.n.01 (763) &  car.n.01 (727) &  kitchen\_utensil.n.01 (132) &  dress.n.01 (199) &  shelter.n.01 (169) &  foodstuff.n.02 (280) &  male\_child.n.01 (853) \\
	 dog.n.01 (688) &  motorcycle.n.01 (564) &  crockery.n.01 (92) &  headdress.n.01 (135) &  restaurant.n.01 (58) &  vegetable.n.01 (48) &  athlete.n.01 (396) \\
	  bird.n.01 (389) &  truck.n.01 (559) &  cutlery.n.02 (82) &  neckwear.n.01 (65) &  outbuilding.n.01 (31) &  edible\_fruit.n.01 (42) &  child.n.01 (333) \\
	  flower.n.01 (44) &  boat.n.01 (499) &  tool.n.01 (72) &  robe.n.01 (27) &  hotel.n.01 (19) &  beverage.n.01 (23) &  creator.n.02 (11) \\
	  rodent.n.01 (27) &  ship.n.01 (38) &  lamp.n.01 (34) &  glove.n.02 (7) &  housing.n.01 (17) &   &  professional.n.01 (5) \\
	 insect.n.01 (12) &   &   &  footwear.n.01 (5) &  place\_of\_worship.n.01 (12) &   &   \\
	  fish.n.01 (11) &   &   &   &   &   &   \\
	\bottomrule
\end{tabular}
	\caption{Overview of our dataset: Collection nodes for each domain (number of instances in parentheses). \textbf{double-check} \label{tab:overview_dataset2}}
\end{table*}

>>>>

We take data from \vgenome \cite{krishna2016visualgenome}, which
% aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
contains a dense region-based labeling of $108k$~images with object descriptions, attributes, and relationships, as well as question-answer pairs, all linked to WordNet synsets \cite{fellbaum1998wordnet}.
\vgenome is suitable for our purpose of collecting names for a relatively large amount of instances of common objects in
naturalistic images, as it has images of varying complexity, with close-ups as well as complex images with many objects.
As common in Computer Vision, objects are identified via bounding boxes (see red boxes in Figure~\ref{fig:cake}).% 
\footnote{We use image and object interchangeably in the following, since we only selected one target object per image (i.e., each object and image in VG is chosen at most once).}

\subsection{Sampling of Instances}

 % of frequent classes/names in  \vgenome, which, at the same time, have been frequently/commonly studied in the psycholinguistic literature. 
%Criteria: From CV: select images depicting objects with relatively frequent names; From CogSci: select objects which have been frequently studied in cognitive science/psychological norming studies; we chose McRae et al. as basis.
We selected seven domains: six from McRae et al.'s feature norms (REF), a dataset widely used in Psycholinguistics that consists of common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}), and \textsc{person}, because it is very frequent category in \vgenome.
% We start from the concepts of McRae et al.'s feature norms (REF), which are common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}) and, as such, have a high overlap with standard datasets of object norming studies (REFS).
% We added the \textsc{person} category because it is very frequent category in \vgenome.

Within each domain, we aimed at collecting instances at different levels in a taxonomy to cover a wide range of phenomena, but it is not straightforward to do so because ontological taxonomies do not align well with the lexicon (for instance, \textit{dog} and \textit{cow} are both mammals, but \textit{dog} has many more common subcategories), and most domains are not organized in a clear taxonomy in the first place (e.g.\ \textsc{home}).
% Standard taxonomies do not align well with name variability; for instance, people use more varied names for types of dogs than for types of cows, while both dogs and cows are mammals.
Instead, we defined a set of synsets that we would use to collect our object instances from \vgenome, balancing variability.
From the set of synsets that match or subsume the concepts in the McRae norms, we kept those that had a high number of \vgenome object instances of different names.
For example, \vgenome instances subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck}, \textsl{goose}, or \textsl{gull} did not have name variants in \vgenome, so we kept \textsl{dog} and \textsl{bird} (which subsumes \textsl{duck}, \textsl{goose}, or \textsl{gull}) as collection synsets.

We then retrieved all VG images depicting an object whose name matches or is subsumed by words in one of these synsets; we refer to these words as \textit{seeds}, and we had XXX\gbt{Carina?} of them.
We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{(REF to tagger)}, or that were multi-word expressions (e.g.,~\textsl{pink bird}). 
We further only considered objects whose bounding box covered an area of~$20-90\%$ of the image.
% We based the definition of our set of nodes on the WN (REF) synsets of the McRae concepts (e.g.,~dog, duck, goose, gull), the nominal WordNet hierarchy, and the frequency distribution of the VG object names' synsets.\footnote{TODO: need to be clear from the general description of VG that the frequ. of instances labeled with the synset of the object name is meant.}

% First, we selected a set of collection node candidates---synsets which match (e.g.,~\textsl{dog, duck, goose, gull}) or subsume (e.g.,~\textsl{mammal, bird}) the McRae synsets\footnote{Specific synset IDs, e.g.,~dog.n.01, are omitted for readability.}. 
% From these candidates we kept those as collection nodes which had a high frequency of VG object instances of different names. For example, VG instances  subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck, goose}, or \textsl{gull} did not have name variants in VG, so we kept \textsl{dog} and \textsl{bird} as collection nodes.

%\paragraph{Collection of instance candidates}
% Goal of above procedure was the collection of instances of selected object classes---our nodes--- whose VG names correspond to or subsume (are hypernyms of) a McRae concept, and whose object names differ, that is, of which we can expect that people possess different names for them (e.g.,~\textsl{duck, goose, gull} for \textsl{bird}).

% \paragraph{Sampling of instances}

Because of the Zipfian distribution of names, and to balance the collection, we sampled instances depending on the size of the seeds: up to 500 instances for seeds with up to 800 objects, and up to 1000 instances for larger seeds. \textbf{double-check}
This yielded a dataset with $31,093$~instances, which was further pruned during annotation (see next subsection).

\gbt{Checked up to here}.

Table~\ref{tab:XXX} gives an overview of the collection synsets, XXX, XXX, grouped into $7$~domains. (\textbf{Report only final dataset, with a note in caption/footnote referring to the checkpoint pruning.})

@@

\begin{table*}
\small
	\begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
	\toprule
	        animals\_plants &               vehicles &                        home &                clothing &                   buildings &                    food &                 people \\
	\midrule
	  ungulate$_1$ (2037) &  aircraft$_1$ (1208) &  furnishing$_2$ (5355) &  shirt$_1$ (968) &  house$_1$ (364) &  dish$_2$ (812) &  woman$_1$ (1768) \\
	 horse$_1$ (833) &  train$_1$ (957) &  vessel$_3$ (525) &  overgarment$_1$ (786) &  bridge$_1$ (297) &  baked\_goods$_1$ (770) &  man$_1$ (1167) \\
	  feline$_1$ (763) &  car$_1$ (727) &  kitchen\_utensil$_1$ (132) &  dress$_1$ (199) &  shelter$_1$ (169) &  foodstuff$_2$ (280) &  male\_child$_1$ (853) \\
	 dog$_1$ (688) &  motorcycle$_1$ (564) &  crockery$_1$ (92) &  headdress$_1$ (135) &  restaurant$_1$ (58) &  vegetable$_1$ (48) &  athlete$_1$ (396) \\
	  bird$_1$ (389) &  truck$_1$ (559) &  cutlery$_2$ (82) &  neckwear$_1$ (65) &  outbuilding$_1$ (31) &  edible\_fruit$_1$ (42) &  child$_1$ (333) \\
	  flower$_1$ (44) &  boat$_1$ (499) &  tool$_1$ (72) &  robe$_1$ (27) &  hotel$_1$ (19) &  beverage$_1$ (23) &  creator$_2$ (11) \\
	  rodent$_1$ (27) &  ship$_1$ (38) &  lamp$_1$ (34) &  glove$_2$ (7) &  housing$_1$ (17) &   &  professional$_1$ (5) \\
	 insect$_1$ (12) &   &   &  footwear$_1$ (5) &  place\_of\_worship$_1$ (12) &   &   \\
	  fish$_1$ (11) &   &   &   &   &   &   \\
	\bottomrule
\end{tabular}
	\caption{Overview of our dataset: Synset nodes for each domain (subscript indicates synset number; number of instances in parentheses). \textbf{double-check} \label{tab:overview_dataset2}}
\end{table*}
